Designing Turk Experiments for Visual Statistical Inference

### 2013-06-14 paper_turk.tex
some writing plans added

\subsection{Data Cleaning}

\subsection{Diversity in the Data}

\begin{figure}[hbtp]
   \centering
       \scalebox{.5}{\includegraphics{turker_country.pdf}}
       \scalebox{.5}{\includegraphics{turker_location.pdf}}       
       \caption{The location of turk workers on the world map shows the geographical diversity of turk workers even though most of the workers come from India and United States.}
       \label{fig:rsq}
\end{figure}

@@

\section{Appendix: What do Turk Workers Pick, $R^2$ or $p$-value?} What do people pick in a lineup plot, p-value or $R^2$? To address this issue we obtain the approximate theoretical relationship between $R^2$ and the power of the classical hypothesis test. Suppose we want to test the significance of the slope ( i.e.,  $H_0: \beta=0$ against $\beta \ne 0$) of a continuous covariate $X$ in  a simple linear regression model setting. Also consider $X \sim N(0,1)$. For a sample of size $n$ this gives us 
\begin{eqnarray*}
Y_i-\bar{Y}& = & \beta_0+\beta_1X_i+\epsilon_i - \beta_0 - \beta_1 \bar{X}- \bar{\epsilon} \\
          & = & \beta_1(X_i-\bar{X})+(\epsilon_i-\bar{\epsilon})
\end{eqnarray*}
Now 
\begin{eqnarray*}
X_i-\bar{X}& = & X_i - \frac1n (X_1 + X_2 + ... + X_i + .....+ X_n) \\
          & = & X_i - \frac1n X_i - \frac1n \sum_{j \neq i}{X_j}\\
          & = & (1-\frac1n)X_i - \frac1n \sum_{j \neq i}{X_j}
\end{eqnarray*}

Thus we have 
\begin{eqnarray*}
E(X_i-\bar{X})^2 & = & (1-\frac1n)EX_i^2 - \left( \frac1n \right )^2 (n-1) EX_j^2 \\
                 & = & (1-\frac1n)^2+ \frac{n-1}{n^2}\\
                 & = & \frac{n-1}{n}
\end{eqnarray*}

Similarly we have

\begin{eqnarray*}
E(\epsilon_i-\bar{\epsilon})^2 & = & (1-\frac1n)E\epsilon_i^2 - \left( \frac1n \right )^2 (n-1) E\epsilon_j^2 \\
                 & = & \left((1-\frac1n)^2+ \frac{n-1}{n^2} \right) \sigma^2 \\
                 & = & \frac{n-1}{n}\sigma^2
\end{eqnarray*}
Finally we have expected total sum of square (SST) as
\begin{eqnarray*}
E\sum_i{(Y_i-\bar{Y})^2} & = & \sum_i E(Y_i-\bar{Y})^2=\sum_i \left [ \beta_1^2 E(X_i-\bar{X})^2 + E(\epsilon_i-\bar{\epsilon})^2 \right] \\
                 & = & \sum_i\left[ \beta_1^2 \frac{n-1}{n}+  \sigma^2 \frac{n-1}{n}\right]\\
                 & = & (n-1)(\sigma^2+\beta_1^2)
\end{eqnarray*}

We know $E(MSE|X) = \sigma^2$ or $E(SSE/n-2)|X = \sigma^2$ which gives the expected residual or error sum of square as $$E \sum_i (Y_i-\hat Y_i)^2=(n-2)\sigma^2$$
Thus we have the expected regression sum of squares $SSR =  (n-1)(\sigma^2+\beta_1^2) - (n-2)\sigma^2 = (n-1) \beta_1^2+\sigma^2$ This gives $$R^2=\frac{(n-1) \beta_1^2+\sigma^2}{ (n-1)(\sigma^2+\beta_1^2)}$$

\begin{figure}[hbtp]
   \centering
       \scalebox{.3}{\includegraphics{scatter_plot_beta_4.pdf}}
       \caption{Scatter plot of data generated for $\beta_0$=6, $\beta_1$=4, sample size $n =300$ and $\sigma = 12$. $R^2$ for this data was obtained as 0.1309 showing that the model could not successfully explain the variation in $Y$. But notice in figure \ref{fig:power_rsq} that power for $\beta$=4 is almost 1. So, Can we conclude that $R^2$ does not have any effect in deciding whether $H_0: \beta_1=0$ should be rejected or not?}
       \label{fig:plot_beta_4}
\end{figure}

\begin{figure}[hbtp]
   \centering
       \scalebox{.35}{\includegraphics{power_300_12.pdf}}
       \caption{Power curve and $R^2$ values for sample size $n =300$ and $\sigma = 12$. Notice that for a small value of $R^2$ (0.1) the power is almost 1.}
       \label{fig:power_rsq}
\end{figure}

\begin{figure}[hbtp]
   \centering
       \scalebox{.35}{\includegraphics{rsquare_contour.pdf}}
       \scalebox{.35}{\includegraphics{rsquare_beta_sigma.pdf}}
       \caption{Contour and surface plots of $R^2$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
       \label{fig:contour_rsq}
\end{figure}

\begin{figure}[hbtp]
   \centering
       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines.pdf}}
       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines1.pdf}}       
       \caption{Relationship of $R^2$ with $\sigma$ and $\beta$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
       \label{fig:rsq}
\end{figure}

>>>>

\subsection{Data Cleaning} Some suggestion about data cleaning based on experimental evidence. What to expect from turk data.

\subsection{Diversity in the Data} Demographics, geographical locations, academic diversity

%\begin{figure}[hbtp]
%   \centering
%       \scalebox{.5}{\includegraphics{turker_country.pdf}}
%       \scalebox{.5}{\includegraphics{turker_location.pdf}}       
%       \caption{The location of turk workers on the world map shows the geographical diversity of turk workers even though most of the workers come from India and United States.}
%       \label{fig:rsq}
%\end{figure}

@@

%
%\section{Appendix: What do Turk Workers Pick, $R^2$ or $p$-value?} What do people pick in a lineup plot, p-value or $R^2$? To address this issue we obtain the approximate theoretical relationship between $R^2$ and the power of the classical hypothesis test. Suppose we want to test the significance of the slope ( i.e.,  $H_0: \beta=0$ against $\beta \ne 0$) of a continuous covariate $X$ in  a simple linear regression model setting. Also consider $X \sim N(0,1)$. For a sample of size $n$ this gives us 
%\begin{eqnarray*}
%Y_i-\bar{Y}& = & \beta_0+\beta_1X_i+\epsilon_i - \beta_0 - \beta_1 \bar{X}- \bar{\epsilon} \\
%          & = & \beta_1(X_i-\bar{X})+(\epsilon_i-\bar{\epsilon})
%\end{eqnarray*}
%Now 
%\begin{eqnarray*}
%X_i-\bar{X}& = & X_i - \frac1n (X_1 + X_2 + ... + X_i + .....+ X_n) \\
%          & = & X_i - \frac1n X_i - \frac1n \sum_{j \neq i}{X_j}\\
%          & = & (1-\frac1n)X_i - \frac1n \sum_{j \neq i}{X_j}
%\end{eqnarray*}
%
%Thus we have 
%\begin{eqnarray*}
%E(X_i-\bar{X})^2 & = & (1-\frac1n)EX_i^2 - \left( \frac1n \right )^2 (n-1) EX_j^2 \\
%                 & = & (1-\frac1n)^2+ \frac{n-1}{n^2}\\
%                 & = & \frac{n-1}{n}
%\end{eqnarray*}
%
%Similarly we have 
%
%\begin{eqnarray*}
%E(\epsilon_i-\bar{\epsilon})^2 & = & (1-\frac1n)E\epsilon_i^2 - \left( \frac1n \right )^2 (n-1) E\epsilon_j^2 \\
%                 & = & \left((1-\frac1n)^2+ \frac{n-1}{n^2} \right) \sigma^2 \\
%                 & = & \frac{n-1}{n}\sigma^2
%\end{eqnarray*}
%Finally we have expected total sum of square (SST) as
%\begin{eqnarray*}
%E\sum_i{(Y_i-\bar{Y})^2} & = & \sum_i E(Y_i-\bar{Y})^2=\sum_i \left [ \beta_1^2 E(X_i-\bar{X})^2 + E(\epsilon_i-\bar{\epsilon})^2 \right] \\
%                 & = & \sum_i\left[ \beta_1^2 \frac{n-1}{n}+  \sigma^2 \frac{n-1}{n}\right]\\
%                 & = & (n-1)(\sigma^2+\beta_1^2)
%\end{eqnarray*}
%
%We know $E(MSE|X) = \sigma^2$ or $E(SSE/n-2)|X = \sigma^2$ which gives the expected residual or error sum of square as $$E \sum_i (Y_i-\hat Y_i)^2=(n-2)\sigma^2$$
%Thus we have the expected regression sum of squares $SSR =  (n-1)(\sigma^2+\beta_1^2) - (n-2)\sigma^2 = (n-1) \beta_1^2+\sigma^2$ This gives $$R^2=\frac{(n-1) \beta_1^2+\sigma^2}{ (n-1)(\sigma^2+\beta_1^2)}$$
%
%
%\begin{figure}[hbtp]
%   \centering
%       \scalebox{.3}{\includegraphics{scatter_plot_beta_4.pdf}}
%       \caption{Scatter plot of data generated for $\beta_0$=6, $\beta_1$=4, sample size $n =300$ and $\sigma = 12$. $R^2$ for this data was obtained as 0.1309 showing that the model could not successfully explain the variation in $Y$. But notice in figure \ref{fig:power_rsq} that power for $\beta$=4 is almost 1. So, Can we conclude that $R^2$ does not have any effect in deciding whether $H_0: \beta_1=0$ should be rejected or not?}
%       \label{fig:plot_beta_4}
%\end{figure}
%
%
%\begin{figure}[hbtp]
%   \centering
%       \scalebox{.35}{\includegraphics{power_300_12.pdf}}
%       \caption{Power curve and $R^2$ values for sample size $n =300$ and $\sigma = 12$. Notice that for a small value of $R^2$ (0.1) the power is almost 1.}
%       \label{fig:power_rsq}
%\end{figure}
%
%
%\begin{figure}[hbtp]
%   \centering
%       \scalebox{.35}{\includegraphics{rsquare_contour.pdf}}
%       \scalebox{.35}{\includegraphics{rsquare_beta_sigma.pdf}}
%       \caption{Contour and surface plots of $R^2$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
%       \label{fig:contour_rsq}
%\end{figure}
%
%\begin{figure}[hbtp]
%   \centering
%       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines.pdf}}
%       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines1.pdf}}       
%       \caption{Relationship of $R^2$ with $\sigma$ and $\beta$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
%       \label{fig:rsq}
%\end{figure}
%
